RSM - Call for papers on data visualization

### 2020-04-20 RSM-paper/manuscript.Rmd
Add new versions of RSM paper Includes accepted version (RSM Revision Submitted)

---
title: "RSM - Call for papers on data visualization"
bibliography: references.bib
csl: ama.csl
output:
  bookdown::word_document2:
      toc: false
      toc_depth: 3
      reference_docx: word-styles-reference-01.docx
  bookdown::pdf_document2:
  bookdown::html_document2:
      toc: true
      toc_depth: 2
---

@@

# Front Matter
__Title: __  
Risk-Of-Bias VISualization (robvis): an R package and Shiny web app for visualizing risk-of-bias assessments

@@

__Authors and Affliations__

@@

Risk of bias; Evidence synthesis; Data visualisation; R

@@

It is now straightforward to produce such a tool, thanks to the availability of powerful computing offerings including R, RStudio and `Shiny` (an R package for building interactive web apps) [@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias Visualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily. While primarily designed for use with the major risk-of-bias assessment tools used in health research (ROB2, ROBINS-I & QUADAS-2), the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.

@@

In order to help users familiarize themselves with the package and its functionality, `robvis` contains built-in example datasets for each template. We illustrate the example data for the RoB 2 tool for assessing risk of bias in randomized trials in Table  \@ref(tab:robdata).

@@

`robvis` contains two main functions. The first, `rob_traffic_light()`, creates a _traffic light plot_. This displays every risk-of-bias judgement in a matrix, with domains along the horizontal and results/studies down the vertical, similar to the data set. The second function, `rob_summary()`, creates a _weighted bar plot_. This shows the proportion of information with each risk-of-bias judgement seperately for each domain in the assessment tool specified.

@@

While `robvis` is a stable package, a range of additional functionality could be added. At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority. For example, a template for ROBIS, the risk-of-bias assessment tool for systematic reviews,[@whiting2016robis] is in developement. Additionally, the `robvis` tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments. However, following user-driven demand, this functionality is in development and will be available in the near future. Finally, we would like to add similar functionality to that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis. The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.

@@

arguments <- data.frame(stringsAsFactors=FALSE,
              argument = c("data", "tool", "colour", "overall", "weighted",
                           "psize"),
     rob_traffic_light = c("X", "X", "X", "", "", "X"),
           rob_summary = c("X", "X", "X", "X", "X", ""),
           Description = c(
"Defines the dataframe containing the summary (domain) level risk-of-bias assessments. See the text and Table 1 for the format expected by `robvis`",
"Defines the risk of bias assessment tool used. The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported. Other tools can be visualized using the generic template (`tool = \"Generic\"`) [Note 1]",
"Defines the colour scheme for the plot. The default is `colour = \"cochrane\"` which uses the \"Cochrane\" (red, yellow, green) colours, while a preset option for a colour-blind friendly palette is also available (`colour = \"colourblind\"`). Alternatively, users can specify their own colour scheme e.g. `colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
"Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure. Default is `overall = FALSE`.",
"Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",
"Defines the size of the points in the traffic light plot. Default is `psize = 20`."))

>>>>

---
title: ""
bibliography: references.bib
csl: ama.csl
output:
  bookdown::word_document2:
      toc: false
      toc_depth: 3
      reference_docx: word-styles-reference-01.docx
  bookdown::pdf_document2:
  bookdown::html_document2:
      toc: true
      toc_depth: 2
---

@@

# Front Matter
__Title: __  
Risk-Of-Bias VISualization (`robvis`): an R package and Shiny web app for visualizing risk-of-bias assessments

@@

__Authors and Affiliations__

@@

Risk of bias; Evidence synthesis; Data visualization; R

@@

It is now straightforward to produce such a tool, thanks to the availability of powerful computing offerings including R, RStudio and `Shiny` (an R package for building interactive web apps) [@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualization),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily. While primarily designed for use with the major risk-of-bias assessment tools used in health research (ROB2, ROBINS-I & QUADAS-2), the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.

@@

In order to help users familiarize themselves with the package and its functionality, `robvis` contains built-in example data-sets for each template. We illustrate the example data for the RoB 2 tool for assessing risk of bias in randomized trials in Table  \@ref(tab:robdata).

@@

`robvis` contains two main functions. The first, `rob_traffic_light()`, creates a _traffic light plot_. This displays every risk-of-bias judgement in a matrix, with domains along the horizontal and results/studies down the vertical, similar to the data set. The second function, `rob_summary()`, creates a _weighted bar plot_. This shows the proportion of information with each risk-of-bias judgement separately for each domain in the assessment tool specified.

@@

While `robvis` is a stable package, a range of additional functionality could be added. At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority. For example, a template for ROBIS, the risk-of-bias assessment tool for systematic reviews,[@whiting2016robis] is in development. Additionally, the `robvis` tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments. However, following user-driven demand, this functionality is in development and will be available in the near future. Finally, we would like to add similar functionality to that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis. The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.

@@

arguments <- data.frame(stringsAsFactors=FALSE,
              argument = c("data", "tool", "colour", "overall", "weighted",
                           "psize"),
     rob_traffic_light = c("X", "X", "X", "", "", "X"),
           rob_summary = c("X", "X", "X", "X", "X", ""),
           Description = c(
"Defines the dataframe containing the summary (domain) level risk-of-bias assessments. See the text and Table 1 for the format expected by `robvis`",
"Defines the risk of bias assessment tool used. The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported. Other tools can be visualized using the generic template (`tool = \"Generic\"`) [Note 1]",
"Defines the colour scheme for the plot. The default is `colour = \"cochrane\"` which uses the \"Cochrane\" (red, yellow, green) colours, while a preset option for a colour-blind friendly palette is also available (`colour = \"colourblind\"`). Alternatively, users can specify their own colour scheme e.g. `colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
"Defines whether to include an additional bar showing the distribution of overall risk of bias judgments in the summary barplot figure. Default is `overall = FALSE`.",
"Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",
"Defines the size of the points in the traffic light plot. Default is `psize = 20`."))
